Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-09-11 forgerard.tex
plowing on

\color{red}
The 68\% credible intervals of $\gamma$ are shown in Figure~\ref{fitz:fig}.
A fit of the output $\gamma$ parameters to the dust model of \citet{1999PASP..111...63F} gives $R^F_V=3.06\pm 0.18$.
\color{black}

@@

\color{red}
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$.  We conclude that the
intrinsic parameter does not arise to compensate for the fact that light-curve shape is not explicitly
contained in our model.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/x1si.pdf}
   \includegraphics[width=2.8in]{output11/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.
The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix.
Assembling
a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
chain, element by element.
For $UBVRI$ the matrix is
\begin{equation}
\begin{pmatrix}
0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
 \end{pmatrix} \text{mag}^2.
 \end{equation}
The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
expressed as the standard deviations and
 correlation matrix
 \begin{equation}
 \begin{pmatrix}
0.066 , 0.033 , 0.022 , 0.050 
  \end{pmatrix} \text{mag}
 \label{color_sd:eqn}
   \end{equation}
 \begin{equation}
\begin{pmatrix}
1.000 & 0.634 & -0.256 & -0.300 \\
0.634 & 1.000 & -0.203 & 0.032 \\
-0.256 & -0.203 & 1.000 & 0.604 \\
-0.300 & 0.032 & 0.604 & 1.000
  \end{pmatrix}.
  \label{color_cor:eqn}
 \end{equation}

@@

@@

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
surprising as they
are strong features in the $B$ band.
Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$
Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, just not as strongly as the equivalent widths,
and  anticipate that in the previous analysis the equivalent widths of CaII and 
SiII would also have shown correlations with color.

>>>>

@@

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.
The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix.
Assembling
a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
chain, element by element.
For $UBVRI$ the matrix is
\begin{equation}
\begin{pmatrix}
0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
 \end{pmatrix} \text{mag}^2.
 \label{mag_cov:eqn}
 \end{equation}
The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
expressed as the standard deviations and
 correlation matrix
 \begin{equation}
 \begin{pmatrix}
0.066 , 0.033 , 0.022 , 0.050 
  \end{pmatrix} \text{mag}
 \label{color_sd:eqn}
   \end{equation}
 \begin{equation}
\begin{pmatrix}
1.000 & 0.634 & -0.256 & -0.300 \\
0.634 & 1.000 & -0.203 & 0.032 \\
-0.256 & -0.203 & 1.000 & 0.604 \\
-0.300 & 0.032 & 0.604 & 1.000
  \end{pmatrix}.
  \label{color_cor:eqn}
 \end{equation}

@@

\color{red}
Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
Our magnitude residuals  given in Eqn.~\ref{mag_cov:eqn} are comparable to those of SALT2
\citep[Fig.\ 8 of][]{2010A&A...523A...7G}, showing no obvious disadvantage from not using $X_1$.
Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
as a function of $X_1$.  For all colors, there appear non-linear correlations between $X_1$ and color residuals,
with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
The SN~Ia time evolution does convey information not captured by the peak-magnitude spectral features used in
the current analysis, and  a linear model may be incapable of doing so.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/x1si.pdf}
   \includegraphics[width=2.8in]{output11/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/residualx1.pdf}
    \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
            of the SALT2 light-curve shape parameter $X_1$.  For reference a dotted line is plotted at zero difference.}
   \label{x1res:fig}}
\end{figure}

\color{red}
The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model.
The posteriors of $\gamma$ are fit to the dust model of \citet{1999PASP..111...63F}, giving
$R^F_V=3.06\pm 0.18$;  Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and the
result of the fit.  Note that  unlike the $R_V$ posteriors, 
the posteriors of $\gamma$ are well-approximated by a normal distribution, which is used for the fit.
\color{black}

@@

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
surprising as they
are strong features in the $B$ band.
Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$
Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
\textcolor{red}{but the equivalent-width corrections are preferred as they give lower residual dispersions $C_c$},
and  anticipate that in the previous analysis the equivalent widths of CaII and 
SiII would also have shown correlations with color.
